---
title: "literallycrying"
format: html
editor: visual
---

Well...I did porifera.\
\
I did it really well.

I did it for hours. Days. Multiple days.

And then it got deleted because I this is my 8th time trying to make a New Project that somehow also successfully Gits. I keep repeating the first steps over and over to make it into a git thing.

So you are not getting my answers because they are gone and at this point I am sobbing.\
\
But update --- I copy-pasted it from an old html link.

UPDATES AGAIN MAX!!! Aspen helped me a lot. I can take no credit for this. I am a 🪱.

# **IamSad-CompThinking1**

## **Computational Thinking 1 🧽 PORIFERA 🧽**

**Q1:** Match the following types of real-world data to their equivalent R type and explain your reasoning.

-   Real world data:

    -   scientific names = character because they are words

    -   the count of plants in a quadrat = integers because they are just normal \#'s

    -   whether or not it rained on a sequence of days = logical, because it's a yes or no situation

    -   and the reaction times of birds to disturbances in seconds = double, numeric.....?

-   R types: logical, integer, numeric, and character

    \-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--

    Q2: In plain english, what does this code chunk do? Two of the lines have mistakes that keep the code from doing what it's supposed to. What are the mistakes and how would you fix them?

```{r}

bird_mass_g <- c(100.1, 99.2, 99.3, NA, 100.0, 101.5, 94.7, 99.2, 108.2) 
# Makes a vector of the numeric sort (>:()) of masses called bird_mass_g


mean_mass <- mean(bird_mass_g)
sd_mass <- sd(bird_mass_g)
# THERE ARE NA'S SO IT CAN'T DO THE MEAN OR THE SD!!!!!!!!! 

# FIXED CODE -- we removed the dastardly NA's 
mean_mass <- mean(bird_mass_g, na.rm = TRUE)        
mean_mass

sd_mass <- sd(bird_mass_g, na.rm = TRUE)
sd_mass 

BIRDZ <- bird_mass_g[!is.na(bird_mass_g)]

is_outlier <- BIRDZ > mean_mass + 3 * sd_mass
# takes the bird masses from bird_mass_g that are greater than the mean_mass of all birds that are + 3 * the standard deviation (3 SD's away from the mean?) and names those values is_outlier

num_outliers <- sum(is_outlier)
# takes the sum of the outliers 
# Returns: [1] NA <-- is this...wrong...? >:(

num_outliers
```

-   Two of the lines have mistakes that keep the code from doing what it's supposed to. What are the mistakes and how would you fix them?

    -   The code cannot calculate mean and SD because there are dastardly NA's involved.

-   What are the types of:

    -   `bird_mass_g` = numeric, double

    -   `is_outlier = logical`

    -   `num_outliers` = integer

\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--

**Q3**

How could you change the first line of code in the following chunk so that `median_count` comes out to `5L`?

```{r}
quad_counts <- c(2L, 19L, 4L, 5L, 5L, 12L, 0L, 7L)
# creates of vector of numbers and L'sx

# Old Version
valid_quads <- c(1, 2, 3, 5, 7) # Median Count = 4

#Changed Version 
valid_quads <- c(2, 3, 5, 6, 7) # Median Count = 5 -- not getting 5L just 5...? 

quad_counts2 <- quad_counts[valid_quads]
# From ChatGPT: This line creates a new vector named quad_counts2 by subsetting the quad_counts vector using the values in the valid_quads vector as indices. In other words, it selects elements from quad_counts at the positions specified by the values in valid_quads.

quad_counts2

median_count <- median(quad_counts2)

median_count

```
